Interoception Scale (Study 2) - Data Cleaning

### 2025-03-09 study2/analysis/1_cleaning.qmd
update 1

@@

@@

Among these, `r sum(is.na(df$MINT_Awareness_RelA_29))` have missing data for the MINT due to a technical error.

>>>>

## Recruitment History

```{r}
#| message: false

# Consecutive count of participants per day (as area)
df |>
  mutate(Date = as.Date(Experiment_StartDate, format = "%Y-%m-%d %H:%M:%S")) |> 
  summarize(N = n(), .by=c("Date", "Recruitment")) |> 
  complete(Date, Recruitment, fill = list(N = 0)) |> 
  mutate(N = cumsum(N), .by="Recruitment") |>
  ggplot(aes(x = Date, y = N)) +
  geom_area(aes(fill=Recruitment)) +
  scale_y_continuous(expand = c(0, 0)) +
  labs(
    title = "Recruitment History",
    x = "Date",
    y = "Total Number of Participants"
  ) +
  see::theme_modern()
```

```{r}
#| message: false

# Table
summarize(df, N = n(), .by=c("Recruitment")) |> 
  arrange(desc(N)) |> 
  gt::gt() |> 
  gt::opt_stylize() |> 
  gt::opt_interactive(use_compact_mode = TRUE) |> 
  gt::tab_header("Number of participants per recruitment source")
```

@@

We removed `r sum(is.na(df$MINT_Awareness_RelA_29))` participants with missing data for the MINT due to a technical error.

df <- filter(df, !is.na(df$MINT_Awareness_RelA_29))
```

@@
